Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection

### 2021-04-20 publication_materials/ms_rbc.tex
IVP error

To derive the quasilinear form, we posit that an arbitrary field $f$ can be represented as the sum of a mean profile (denoted by $\bar{f}$) and a perturbation function (denoted by $f'$).
\begin{align}
    \vec{u}(x, z, t) &= \vec{u'}(x, z, t) \label{EQ:reynolds_dc_u}\\
    &= u'(x, z, t)\hat{x} + w'(x, z, t)\hat{z} \\
    T(x, z, t) &= \bar{T}(z, t) + T'(x, z, t) \label{EQ:reynolds_dc_T}\\
    p(x, z, t) &= \bar{p}(z, t) +  p'(x, z, t) \label{EQ:reynolds_dc_p}.
\end{align}
where the mean-velocity components vanish due to incompressibility and symmetry. Perturbations are defined to have no horizontal-average
\begin{equation}
    \langle f'(x, z, t) \rangle_x \equiv \int_{0}^4 f'(x, z, t) dx = 0.
\end{equation}
%Assuming the existance of nontrivial solutions, we also fix the volume-average over the entire domain
%\begin{equation}
%  \langle T'^2 \rangle_{\mathcal{D}} = 1
%\end{equation}
%thereby alleviating any ambiguity in $A(t)$. 
Substituting \eq{EQ:reynolds_dc_T} into \eq{EQ:motion3} and taking the horizontal-average reduces the system to a simple initial value problem (IVP) for $\bar{T}$
\begin{equation}
  \frac{\partial \bar{T}}{\partial t} + \langle w'T' \rangle_x = \mathcal{P}  \frac{\partial^2 \bar{T}}{\partial z^2}, \label{EQ:T0_IVP}
\end{equation}
with associated boundary conditions $\bar{T}(-1/2, t) = 1/2$ and $\bar{T}(1/2, t) = -1/2$. It should be noted that we could obtain a similar IVP for $u$ by breaking symmetry and considering some nontrivial mean horizontal flow $\bar{u}(z, t)$. However we must have $\bar{w}(z, t) = 0$ due to incompressibility.

@@

\note{This last paragraph is somewhat confusing to me. I think it's dangerous to say that we can predict Nu-Ra scaling using anything other than DNS or experiments. Why would 1D boundary-layer predictions give 2D equilibria? Right now we're using a 1D boundary-layer prediction.}
We cannot use our reduced quasilinear model to predict $\Nu \sim\Ra^{\beta}$ for large $\Ra$ without some complementary stability constraint. 
The eigenvalues of DNS data might provide an informative stability constraint (we could find MUTE and compare them with DNS data), but this would be self-defeating in general. 
Instead we seek to combine reduced models to approximate $\beta$ without DNS. Under the marginal-stability constraint, we found that MSTE exhibit classical Malkus scaling, having marginally-stable boundary layers. 
We could instead require that the eigenvalues of MUTE agree with the eigenvalues of the analytic 1D boundary layer predictions of \cite{Shishkina, Zhang_20} (which remain in development), allowing us to refine and expand these estimates into 2D MUTE. 
The process for finding such MUTE would not involve DNS. Equilibria would satisfy only the quasilinear problem and stability constraint. 
They ought to agree with DNS data more than MSTE, ideally having slower flows. 
This is reasonable to expect because accurate boundary layer approximations and DNS data should have similar stability characteristics. 
We also observed that MSTE have marginally stable boundary layers, so it would be reasonable to place a hypothetical stability constraint on MUTE based on boundary layer approximations.
By definition, MUTE are unstable and would likely admit more diffuse boundary layer structures, requiring smaller $A^2(t)$ (less advection) to satisfy the stability constraint and thereby reducing $\Nu$, $\langle |\vec{u}|^2 \rangle_{\mathcal{D}}$ and possibly $\beta$.

>>>>

To derive the quasilinear form, we posit that an arbitrary field $f$ can be represented as the sum of a mean profile (denoted by $\bar{f}$) and a perturbation function (denoted by $f'$).
\begin{align}
    \vec{u}(x, z, t) &= \vec{u'}(x, z, t) \label{EQ:reynolds_dc_u}\\
    &= u'(x, z, t)\hat{x} + w'(x, z, t)\hat{z} \\
    T(x, z, t) &= \bar{T}(z, t) + T'(x, z, t) \label{EQ:reynolds_dc_T}\\
    p(x, z, t) &= \bar{p}(z, t) +  p'(x, z, t) \label{EQ:reynolds_dc_p}.
\end{align}
where the mean-velocity components vanish due to incompressibility and symmetry. Perturbations are defined to have no horizontal-average
\begin{equation}
    \langle f'(x, z, t) \rangle_x \equiv \int_{0}^4 f'(x, z, t) dx = 0.
\end{equation}
%Assuming the existance of nontrivial solutions, we also fix the volume-average over the entire domain
%\begin{equation}
%  \langle T'^2 \rangle_{\mathcal{D}} = 1
%\end{equation}
%thereby alleviating any ambiguity in $A(t)$. 
Substituting \eq{EQ:reynolds_dc_T} into \eq{EQ:motion3} and taking the horizontal-average reduces the system to a simple initial value problem (IVP) for $\bar{T}$
\begin{equation}
  \frac{\partial \bar{T}}{\partial t} + \frac{\partial}{\partial z} \langle w'T' \rangle_x = \mathcal{P} \frac{\partial^2 \bar{T}}{\partial z^2}, \label{EQ:T0_IVP}
\end{equation}
with associated boundary conditions $\bar{T}(-1/2, t) = 1/2$ and $\bar{T}(1/2, t) = -1/2$. It should be noted that we could obtain a similar IVP for $u$ by breaking symmetry and considering some nontrivial mean horizontal flow $\bar{u}(z, t)$. However we must have $\bar{w}(z, t) = 0$ due to incompressibility.

@@

\note{This last paragraph is somewhat confusing to me. I think it's dangerous to say that we can predict Nu-Ra scaling using anything other than DNS or experiments. Why would 1D boundary-layer predictions give 2D equilibria? Right now we're using a 1D boundary-layer prediction.}
We cannot use our reduced quasilinear model to predict $\Nu \sim\Ra^{\beta}$ for large $\Ra$ without some complementary stability constraint. 
The eigenvalues of DNS data might provide an informative stability constraint (we could find MUTE and compare them with DNS data), but this would be self-defeating in general. 
Instead we seek to combine reduced models to approximate $\beta$ without DNS. Under the marginal-stability constraint, we found that MSTE exhibit classical Malkus scaling, having marginally-stable boundary layers. 
We could instead require that the eigenvalues of MUTE agree with the eigenvalues of the analytic 1D boundary layer predictions of \cite{Shishkina, Zhang_20} (which remain in development), allowing us to refine and expand these estimates into 2D MUTE. 
The process for finding such MUTE would not involve DNS. Equilibria would satisfy only the quasilinear problem and stability constraint. 
They ought to agree with DNS data more than MSTE, ideally having slower flows. 
This is reasonable to expect because accurate boundary layer approximations and DNS data should have similar stability characteristics. 
We also observed that MSTE have marginally stable boundary layers, so it would be reasonable to place a hypothetical stability constraint on MUTE based on boundary layer approximations.
By definition, MUTE are unstable and would likely admit more diffuse boundary layer structures, requiring smaller $A^2$ (less advection) to satisfy the stability constraint and thereby reducing $\Nu$, $\langle |\vec{u}|^2 \rangle_{\mathcal{D}}$ and possibly $\beta$.
